---
title: "Defining Custom Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Defining Custom Palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`vintalisation` reads palettes from `inst/palettes.yml` when the package loads.
Each entry contains a key, a vector of colours, and optional metadata.

```yaml
bol:
  colours: ["#0046BE", "#FFD200", "#333333"]
  meta: {brand: bol}
```

## Adding a palette

1. Add a new block at the end of `inst/palettes.yml`.
2. Reload the package (e.g., `devtools::load_all()`).
3. Verify with `show_palette("your_name")`.

```{r, eval=FALSE}
new_palette:
  colours: ["#101010", "#f5a623", "#50e3c2"]
  meta: {brand: custom}
```

## Testing the palette

```{r, message=FALSE}
library(vintalisation)
library(ggplot2)

palette_name <- "adevinta_brand_1"
ggplot(mpg, aes(class, fill = manufacturer)) +
  geom_bar() +
  scale_fill_my_palette(palette_name) +
  theme_custom()
```

## Programmatic access

Use `get_colors()` when you need to manipulate colour vectors directly.

```{r}
head(get_colors("adevinta_brand_1"))
head(get_colors(pattern = "^partner"))
```

You can also serialize palettes back to YAML or JSON using any preferred method once obtained as plain vectors.
