---
title: "Getting Started with vintalisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with vintalisation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

``` r
# install.packages("devtools")
devtools::install_github("aalvarezperez/vintalisation")
```

For local development, install from the working tree:

``` r
devtools::install_local("/path/to/vintalisation", build = TRUE, upgrade = "never")
```

```{r setup, message=FALSE}
library(vintalisation)
library(ggplot2)
```

## Inspecting palettes

```{r show-palette}
show_palette("adevinta_brand_1")
```

`get_palette()` returns a palette function you can pass to other tooling:

```{r get-palette}
get_palette("bol_brand_1")(10)
```

## Scales and themes

```{r scales}
p <- ggplot(mtcars, aes(factor(cyl), fill = factor(gear))) +
  geom_bar() +
  scale_fill_my_palette("studio_accessibility_1") +
  theme_custom("marktplaats")
p
```

## Manychat preset (typography + colours)

```{r manychat, eval=FALSE}
ggplot(mtcars, aes(factor(cyl), fill = factor(gear))) +
  geom_bar() +
  scale_fill_manychat() +
  theme_manychat()
```

Switch to dark mode while keeping the same data and mappings:

```{r dark-mode, eval=FALSE}
p + my_dark_mode()
```

## Saving plots

Use `make_plot()` to enforce consistent dimensions and DPI.

```{r eval=FALSE}
make_plot("mtcars-gears.png")
```

This writes to `./visualisations` relative to the current working directory.
